\documentclass[12pt]{article}

\usepackage{pdfsync}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage[T1]{fontenc}

\graphicspath{{./figures/}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\d}{\mathrm{d}}
\newcommand{\vv}[1]{\boldsymbol{#1}}
\newcommand{\cB}{B}
\newcommand{\cA}{A}
\newcommand{\cC}{C}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\section{Derivation of the Equations of Motion
}\label{Derivation of the Equations of Motion
}
\subsection{Some highlights of Hamilton's Principle}
\subsection{Derivation of the Equations of Motion}
We define the kinetic energy density 
\[ \mathcal{T}(\mathbf{y}_t) = \frac{\ro S}{2} \mathbf{r}_t \cdot \mathbf{r}_t + \frac{\ro I}{2}\teta_t ^2,
\]
where $\ro$S is the linear mass density and $ro$I the linear moment of inertia.
Under the action of forces, the elastic rod-like filament suffers deformations, which we assume to be planar. Whenever these deformations occur, it will be a contact force \textbf{n}(s,t) exerted by the material of [s,1] on that of [0,s). \textbf{n}(s,t) is assumed to lie to the (\textbf{e_1,e_2})-plane, so that it has the form
\[  \mathbf{n}(s,t)= N(s,t) \mathbf{a}(s,t) + H(s,t)\mathbf{b} (s,t).
\]
Let \mathbf{m}(s,t) be the contact couple exerted by the material of [s,1] on tha of [0,s). We assume that \mathbf{m} is perpendicular to the (\mathbf{e_1,e_2})-plane so that it has the form
\[ 
\mathbf{m}(s,t) = M(s,t)\mathbf{e}_3.
\]

We assume that the material of the rod is viscoelastic causing internal energy dissipation and having constitutive equations of the form
\[  N (s,t)=  \hat{N}(\nu (s,t),\eta (s,t)) + \tilde{A} \nu_t (s,t)
\]
\[  H (s,t)=  \hat{H}(\nu (s,t),\eta (s,t)) + \tilde{B} \eta_t (s,t)
\]
\[  M (s,t)=  \hat{M}(\nu (s,t),\eta (s,t), \mu(s,t)) + \tilde{C} \mu_t (s,t),
\]
where $\^{N}$,$\^{H}$,$\^{M}$ are given functions on (0,$\infty$) $\textmultiply$ $\textcolonmonetary{R}$ $\textmultiply$ $\textcolonmonetary{R}$ and where $\tilde{A}$, $\tilde{B}$, $\tilde{C}$ are positive constants.
\\
We model this by introducing the elastic potential density  as
\[ \mathcal{U}(\mathbf{y}) = \frac{\cA}{2} (\nu - \nu_0)^2
+ \frac{\cC}{2} (\eta - \eta_0 )^2
+ \frac{\cB}{2} (\mu -\alpha)^2,
\]
where $\alpha$ = $\alpha$(s,t) is \emph{spontaneous curvature}, $\nu$ = $\nu$(s,t) describes the stretch, $\eta$ = $\eta$(s,t) defines the shear strain and $\cA$, $\cB$, $\cC$ represent respectively the stretch stiffness, the bending stiffness and the shear stiffness. 
This formulation takes into account that we are dealing with a \emph{compressible} viscoelastic medium that has the ability to actively modify its spontaneous curvature.
\\
Along with the elastic potential we introduce the internal energy dissipation density  and the dissipative force associated as 
\[ \mathcal{D}_{diss}(\mathbf{y}_t) = \frac{\tilde{A}}{2}\left|\mu_t\right|^2 + \frac{\tilde{B}}{2}\left|\eta_t\right|^2
+ \frac{\tilde{C}}{2}\left|\nu_t\right|^2,
\]

\[
\mathbf{Q}_{diss}= (\tilde{A}(\nu_t)_s,\tilde{B}(\eta_t)_s,\tilde{A}(\mu_t)_s).
\]
When immersed in a fluid, if we use \emph{resistive force theory},
then the external energy dissipation density and the force applied by fluid on the rod can be modeled as
\[ \mathcal{D}_{ext}(\mathbf{y}_t)= -(\xi_\parallel\left|\mathbf{r}_t\cdot\mathbf{\tau}\right|^2 + \xi_\perp \left|\mathbf{r}_t\cdot\mathbf{P}\right|^2),
\]

\[\mathbf{Q}_{ext} = -( \xi_\parallel (\mathbf{r}_t\otimes\mathbf{\tau})\mathbf{\tau} + \xi_\perp (\mathbf{r}_t\otimes\mathbf{P})\mathbf{P}),
\]
where $\xi_\parallel$ and $\xi_\perp$ are local friction coefficients fort tangential and normal motion, respectively.
We deal with the dissipative forces by means of virtual work terms
\[\delta W = \delta W_{diss} + \delta W_{ext} = (\mathbf{Q}_{diss}+\mathbf{Q}_{ext})\cdot\mathbf{y}.\]







\end{document}
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  